Parsing Tweets into Universal Dependencies

### 2017-12-03 paper.tex
revise all, change some comments

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines \yicomment{including tokenization, POS tagging and parsing? (need to mention the annotation process/pipeline system not only consists parsing in abstract)}, we create
a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreement
among our annotations and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To overcome the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 transition-based parsers into a single one. Our
parser achieves an improvement of 2.6 in LAS over \nascomment{which
  comparison is this?}\yjcomment{my bad, it was fixed.} the baseline
and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
\end{abstract}

\section{Introduction}
NLP for social media messages \yicomment{texts?} is challenging, both \yicomment{not only} because domain
adaptation is required, but also because \yicomment{delete `because' ?} creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{AAAIW113912} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
Stanford dependencies were converted afterwards in their work  \nascomment{by who?}\yjcomment{by themselves}. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose \yicomment{believe?} that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we introduce a new tweet treebank of 55,607 tokens that follows the UD
guidelines, but also contends with social media-specific challenges that were not
covered by UD guidelines. Our annotation includes 
tokenization, part-of-speech (POS) tags, and (labeled) \yicomment{no need for parenthesis} universal dependencies.
We characterize the disagreement among our annotations \yicomment{annotation(s) and disagreement(s). check abstract, same sentence, different singularity/plurality. I think should be `disagreement' and `annotations'} and find that
consistent annotation \yicomment{again, it needs to be the same all the time at least for me.} is still challenging to deliver even with
the extended guidelines.

@@

We release our dataset and our \yicomment{delete `our'} system as open-source software \yicomment{delete `as open-source software'?} at
\url{http://anonymized}.

@@

We first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
which is \yicomment{was} the largest \yicomment{unlabelled} Twitter dependencies annotation
(\S\ref{sec:tweebank}).
Then we introduce the differences in our tokenization
(\S\ref{sec:tok-anno}) and part-of-speech (\S\ref{sec:pos-anno}) (re)annotation with \citet{ICWSM101540} and 
\citet{gimpel-EtAl:2011:ACL-HLT2011}, respectively, on which {\sc Tweebank v1} was built. 
We describe our effort of adapting the
UD conventions to cover tweet-specific constructions (\S\ref{sec:ud-tweet}). 
Finally, we present our process of creating a new tweet treebank, {\sc
  Tweebank v2}, and characterize
the difficulties in reaching consistent annotations (\S\ref{sec:anno-process}).

@@

The annotation effort we describe stands in contrast to \yicomment{the?} previous work
by \newcite{kong-EtAl:2014:EMNLP2014}.  Their aim was the rapid
development of a dependency parser for tweets, and to that end they
contributed a new annotated corpus, \textsc{Tweebank}, consisting of
929 tweets.  Their annotations added \yicomment{unlabelled} dependencies to a portion of the data
annotated with POS tags by 
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT} after rule-based tokenization \citep{ICWSM101540}.
Kong et al.~also contributed a system for parsing;
we defer the discussion of their parser to \S\ref{sec:parsing}.

@@

\subsection{Tokenization}\label{sec:tok-anno}
Our tokenization strategy lies between the strategy of
\citet{ICWSM101540} and that of UD.
There is a significant \yicomment{significant? not really} tradeoff between preservation of original tweet content and respecting
the UD guidelines.

The regex-based tokenizer of \citet{ICWSM101540}---which was 
originally designed for an exploratory search interface called
TweetMotif, not for NLP---preserves most whitespace-delimited tokens, including 
hashtags, at-mentions, emoticons, and unicode glyphs. 
They also treat contractions and acronyms as whole tokens and do not split them.
UD
tokenization,\footnote{\url{http://universaldependencies.org/u/overview/tokenization.html}}
in order to better serve dependency annotation, treats each syntactic word as a token.
They therefore more aggressively split
clitics from contractions (e.g., {\it  gonna} is tokenized as {\it gon} and {\it na}; {\it its}
is tokenized as {\it it} and {\it s} when {\it s} is a copula)\yicomment{I think the examples are not contractions (can't), is there a name for such words?}. But acronyms are not touched
in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
and left acronyms like {\em idc} as a single token. \nascomment{unless we make a change, I think we need to say
  here that acronyms like \emph{idc} are left as a single token}
\yjcomment{mentioned acronymns, we don't have the problem of normalization, cause
normalization was just annotated for data study.}

In the different direction of splitting tokens, UD guidelines also suggest to merge \yicomment{suggest merging?}
{\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
cases. We witnessed a small number of tweets that contain multi-token words
(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
Such tokens only account for 0.067\% and we use the UD
  {\it goeswith} relation to resolve these cases in the dependency annotations.

@@

Before turning to UD \yicomment{dependencies} annotations, we (re)annotated the data with 
POS \yicomment{tags}, for consistency with other UD efforts,
which adopt the universal POS tagset of \newcite{PETROV12.274}.
% The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
% Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
In some cases, conflicts arose between the UD English 
treebank conventions \cite[][UD\_English]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT}.  \yicomment{The conflicts should refer to a {\bf noncorresponding tag} from that of gimpel to UDEnglish, cuz they dont have the same tagset.} In these cases, we always
conformed to UD, enabling consistency (e.g., when we exploit the
existing UD\_English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
  other} ({\tt X}) and {\tt +} is tagged as {\it symbol} ({\tt SYM})
rather than {\it conjunction} ({\tt CCONJ}).  
% Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.
% By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}

Tokens that do not have a syntactic function (discussed at greater
length in the next section) were usually annotated as \emph{other}
(\texttt{X}), except for emoticons, which are tagged as \emph{symbol}
(\texttt{SYM}), following UD\_English.

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{idc}
(abbreviating ``I don't care'')
 and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms? \yicomment{this sentence should be deleted} \yicomment{As we already know from previous sections, \emph{idc} is not tokenized and tagged as verb, we follow ...}
We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
syntax as a single word without normalization. Their syntactic functions
are decided according to their context. \citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
in social media text and argued that such normalization is problematic.
Our solution to the syntax of abbreviations follows the spirit of his argument. Because abbreviations which clearly carry
syntactic functions only constitute 0.06\% of the tokens in our
dataset, we believe that normalization is an unnecessarily complicated step.\yicomment{this should be moved to tokenization section, but we can mention again here for emphasizing.}
% \nascomment{maybe we owe citations to
%   \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
%   better papers to cite}

@@

It is important to note that these types may, in some
contexts, have syntactic functions.
For example, besides being a discourse marker, \emph{RT} can
abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
used as content words within a sentence\yicomment{at-mentions can be a normal vocative proper noun}; see Figure
\ref{fig:informal-toks}.  Therefore, the criteria for \yicomment{whether} annotating a
token as non-syntactic must be context-dependent.
%To our knowledge, this issue has not previously been addressed in UD
%annotation efforts \nascomment{check!}\yjcomment{it's not safe to claim that.}.

@@

\begin{itemize}
\item For the at-mentions in retweet constructions, we attach them to their retweet markers. We will discuss our choice in the following paragraph;
\item For the rest non-syntactic tokens, if one token is within a sentence that has a clear predicate, it will be attached to this predicate. If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
%\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
\item Non-syntactic tokens are mostly labeled as {\it discourse}, but
  URLs are always labeled as {\it list}, following the UD\_English dataset.
%\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
\end{itemize}

@@

\paragraph{Retweet construction.} Figure \ref{fig:non-syn-toks} shows
an example of the retweet construction (\emph{RT @coldplay :}).  This
might be treated as a verb phrase, with \emph{RT} as a verb and the
at-mention as its object.  This solution would lead to an uninformative root
word and, since this expression is idiomatic to Twitter, might create
unnecessary confusion for downstream applications aiming to identify
the main predicate(s) of a tweet.  We therefore treat the whole
expression as non-syntactic, including assigning the \emph{other}
(\texttt{X}) part of speech to both \emph{RT} and \emph{@coldplay},
attaching the at-mention to \emph{RT} with the \emph{discourse}
label and the colon to \emph{RT} with the \emph{punct}(uation) label,
and attaching \emph{RT} to the predicate of the following sentence\yicomment{since we have introduced retweet at-mentions in the non-syntactic tokens, here we can just briefly justify our choice.}.

@@

\paragraph{Constructions handled by UD.}  A number of constructions
that are especially common in tweets are well handled by UD
conventions: ellipsis, irregular word orders, and paratactic sentences \yicomment{or phrases/component}
not explicitly delineated by punctuation.

@@

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is an at-mention %(followed by a colon \nascomment{?})
as a sign that a tweet is a reply to a tweet by the mentioned user\yicomment{not necessary, can be just mentioning somebody. should be careful to say it. We can say this construction include 1. reply;  2. mention sb. Both cases are similar to general vocative proper noun case in standard texts}.  We
treat these at-mentions as vocative expressions, labeling them as
\emph{proper noun} (\texttt{PROPN})\yicomment{here is confusing that PROPN could be a label in dependencies. We can say in POS sections that the decisions on some twitter specific tokens can be made only analyzing syntax together.} and attaching them to the
following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example) \yicomment{just as UD guidelines}.

@@

\subsection{\sc Tweebank v2}\label{sec:anno-process}
Following the guidelines presented above, we create a new annotated\yicomment{del?} Twitter \yicomment{Twitter dependency} treebank, which we call {\sc Tweebank v2}.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the \yicomment{general} UD
annotation conventions and our guidelines \yicomment{specifically for annotating tweets}.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and
parser were trained on the annotated data from the first stage (1,050 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. Finally, an extra
layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)} was manually annotated for data
analysis purposes. For example, ``idc'' is annotated as
`I\_don't\_care' and `4 my FAM' is as `for my familiy'.
Such normalization doesn't change our tokenization annotation. \yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them. Good story :)}\yjcomment{add ``a tokenizer''}

@@

We trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English training dataset
and tested on the \textsc{Tweebank v2} test set. 
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with the UD pipe, we use LSTM
instead of GRU in our model and we also use a larger size of hidden units (64 against 20),
which has stronger representation power. \nascomment{we need to say what their model was;
  why does ours work better?  from their paper, it seems that they
  used a GRU instead of an LSTM ... is that all?  do we win because of
better tuning, or what?}\yjcomment{done.}
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

Results of the \citet{owoputi-EtAl:2013:NAACL-HLT}  with non-greedy
inference on automatically tokenized data
are shown in  Table \ref{tbl:pos-result-vs-tok}.  We see that errors
in tokenization do propagate, but tagging performance is above 93\%
with our tokenizer.

@@

\paragraph{Ensemble.}  Due both to ambiguity in the training
data---which most loss functions are not robust to \citep{Frnay2014ClassificationIT}, including the log loss we use, following
\citet{ballesteros-dyer-smith:2015:EMNLP}---and due to the instability
of neural network training, we follow \citet{Dietterich2000} and
consider an ensemble of twenty parsers trained using different random
initialization.  To parse at test time, the transition probabilities of the twenty
members of the ensemble are averaged.  The result achieves LAS of
79.4, outperforming all three systems above (Table~\ref{tbl:parse-result}).
However, ensembling 20 parsers also significantly slows down the parsing
speed and leads to the slowest system in our comparison.

>>>>

\begin{document}
\maketitle
\begin{abstract}
We study the problem of analyzing tweets with
universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
special constructions in tweets. Using the extended guidelines \yicomment{including tokenization, POS tagging and parsing? (need to mention the annotation process/pipeline system not only consists parsing in abstract)}, we create
a new tweet treebank ({\sc Tweebank v2}), which has 3,550 tweets\yicomment{add tweet \#} and 55,607 tokens with
labeled attachments. 
It is more than four times larger than the (unlabeled) {\sc Tweebank
  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
We characterize the disagreement
among our annotations and show that it is challenging to deliver
consistent annotation due to ambiguity in
understanding and explaining tweets. Using the new treebank,
we build a pipeline system to parse raw tweets into UD. To overcome the
annotation noise without sacrificing computational efficiency, we propose a new
method to distill an ensemble of 20 transition-based parsers into a single one. Our
parser achieves an improvement of 2.6 in LAS over \nascomment{which
  comparison is this?}\yjcomment{my bad, it was fixed.} the baseline
and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
\end{abstract}

\section{Introduction}
NLP for social media messages is challenging, both because domain
adaptation is required, but also because creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{AAAIW113912} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
Stanford dependencies were converted afterwards in their work  \nascomment{by who?}\yjcomment{by themselves}. 
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
consistent annotation across different languages. To allow such
consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
the syntax of tweets can benefit from such adaptability. In this paper,
we introduce a new tweet treebank of 55,607 tokens that follows the UD
guidelines, but also contends with social media-specific challenges that were not
covered by UD guidelines. Our annotation includes 
tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
We characterize the disagreement among our annotations \yicomment{annotation(s) and disagreement(s). check abstract, same sentence, different singularity/plurality. I think should be `disagreement' and `annotations'} and find that
consistent annotation \yicomment{annotations?} is still challenging to deliver even with
the extended guidelines.

@@

We release our dataset and our system as open-source software at
\url{http://anonymized}.

@@

We first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
which is \yicomment{was?} the largest \yicomment{unlabelled?} Twitter dependencies annotation
(\S\ref{sec:tweebank}).
Then we introduce the differences in our tokenization
(\S\ref{sec:tok-anno}) and part-of-speech (\S\ref{sec:pos-anno}) (re)annotation with \citet{ICWSM101540} and 
\citet{gimpel-EtAl:2011:ACL-HLT2011}, respectively, on which {\sc Tweebank v1} was built. 
We describe our effort of adapting the
UD conventions to cover tweet-specific constructions (\S\ref{sec:ud-tweet}). 
Finally, we present our process of creating a new tweet treebank, {\sc
  Tweebank v2}, and characterize
the difficulties in reaching consistent annotations (\S\ref{sec:anno-process}).

@@

The annotation effort we describe stands in contrast to \yicomment{the?} previous work
by \newcite{kong-EtAl:2014:EMNLP2014}.  Their aim was the rapid
development of a dependency parser for tweets, and to that end they
contributed a new annotated corpus, \textsc{Tweebank}, consisting of
929 tweets.  Their annotations added \yicomment{unlabelled?} dependencies to a portion of the data
annotated with POS tags by 
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT} after rule-based tokenization \citep{ICWSM101540}.
Kong et al.~also contributed a system for parsing;
we defer the discussion of their parser to \S\ref{sec:parsing}.

@@

\subsection{Tokenization}\label{sec:tok-anno}
Our tokenization strategy lies between the strategy of
\citet{ICWSM101540} and that of UD.
There is a significant \yicomment{significant?} tradeoff between preservation of original tweet content and respecting
the UD guidelines.

The regex-based tokenizer of \citet{ICWSM101540}---which was 
originally designed for an exploratory search interface called
TweetMotif, not for NLP---preserves most whitespace-delimited tokens, including 
hashtags, at-mentions, emoticons, and unicode glyphs. 
They also treat contractions and acronyms as whole tokens and do not split them.
UD
tokenization,\footnote{\url{http://universaldependencies.org/u/overview/tokenization.html}}
in order to better serve dependency annotation, treats each syntactic word as a token.
They therefore more aggressively split
clitics from contractions (e.g., {\it  gonna} is tokenized as {\it gon} and {\it na}; {\it its}
is tokenized as {\it it} and {\it s} when {\it s} is a copula)\yicomment{are words like gonna called contractions, or do they have another term?}. But acronyms are not touched
in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
and left acronyms like {\em idc} as a single token. \nascomment{unless we make a change, I think we need to say
  here that acronyms like \emph{idc} are left as a single token}
\yjcomment{mentioned acronymns, we don't have the problem of normalization, cause
normalization was just annotated for data study.}

In the different direction of splitting tokens, UD guidelines also suggest to merge
{\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
cases. We witnessed a small number of tweets that contain multi-token words
(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
Such tokens only account for 0.067\% and we use the UD
  {\it goeswith} relation to resolve these cases in the dependency annotations.

@@

Before turning to UD annotations, we (re)annotated the data with 
POS \yicomment{tags?}, for consistency with other UD efforts,
which adopt the universal POS tagset of \newcite{PETROV12.274}.
% The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
% Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
In some cases, conflicts arose between the UD English 
treebank conventions \cite[][UD\_English]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT}.  \yicomment{The conflicts should refer to a {\bf noncorresponding tag} from that of gimpel to UDEnglish, cuz they dont have the same tagset.} In these cases, we always
conformed to UD, enabling consistency (e.g., when we exploit the
existing UD\_English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
  other} ({\tt X}) and {\tt +} is tagged as {\it symbol} ({\tt SYM})
rather than {\it conjunction} ({\tt CCONJ}).  
% Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.
% By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}

Tokens that do not have a syntactic function (discussed at greater
length in the next section) were usually annotated as \emph{other}
(\texttt{X}), except for emoticons, which are tagged as \emph{symbol}
(\texttt{SYM}), following UD\_English, seen in Figure \ref{fig:non-syn-toks} as an example.

@@

\paragraph{Acronym abbreviations.}  How should we syntactically
analyze acronym tokens like \emph{idc}
(abbreviating ``I don't care'')
 and \emph{rn} (``right now'')?  Should
they be decomposed into their component words, and if so should those
words be ``normalized'' into explicitly spelled out intermediate
forms? \yicomment{this sentence should be deleted or moved to tokenization?} \yicomment{As we already know from previous sections, \emph{idc} is not tokenized and tagged as verb, we follow ...} \yicomment{Normalization is discussed in the 2.5.2 Annotation Process. Actually we did do normalization, but just as auxiliary info, didn't use it for any model.}
We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
syntax as a single word without normalization. Their syntactic functions
are decided according to their context. \citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
in social media text and argued that such normalization is problematic.
Our solution to the syntax of abbreviations follows the spirit of his argument. Because abbreviations which clearly carry
syntactic functions only constitute 0.06\% of the tokens in our
dataset, we believe that normalization is an unnecessarily complicated step.\yicomment{Again we did normalization!}
% \nascomment{maybe we owe citations to
%   \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
%   better papers to cite}

@@

It is important to note that these types may, in some
contexts, have syntactic functions.
For example, besides being a discourse marker, \emph{RT} can
abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
used as content words within a sentence\yicomment{at-mentions can be a normal vocative proper noun}; see Figure
\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
token as non-syntactic must be context-dependent.
%To our knowledge, this issue has not previously been addressed in UD
%annotation efforts \nascomment{check!}\yjcomment{it's not safe to claim that.}.

@@

\begin{itemize}
%\item For the at-mentions in retweet constructions, we attach them to their retweet markers. We will discuss our choice in the following paragraph;
\item If one syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate. Retweet construction is a special case and we will discuss our choice in the following paragraph
\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
%\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
\item Non-syntactic tokens are mostly labeled as {\it discourse}, but
  URLs are always labeled as {\it list}, following the UD\_English dataset.
%\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
\end{itemize}

@@

\paragraph{Retweet construction.} Figure \ref{fig:non-syn-toks} shows
an example of the retweet construction (\emph{RT @coldplay :}).  This
might be treated as a verb phrase, with \emph{RT} as a verb and the
at-mention as its object\yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}.  This solution would lead to an uninformative root
word and, since this expression is idiomatic to Twitter, might create
unnecessary confusion for downstream applications aiming to identify
the main predicate(s) of a tweet.  We therefore treat the whole
expression as non-syntactic, including assigning the \emph{other}
(\texttt{X}) part of speech to both \emph{RT} and \emph{@coldplay},
attaching the at-mention to \emph{RT} with the \emph{discourse}
label and the colon to \emph{RT} with the \emph{punct}(uation) label,
and attaching \emph{RT} to the predicate of the following sentence.
%\yicomment{since we have introduced retweet at-mentions in the non-syntactic tokens, here we can just briefly justify our choice.}.

@@

\paragraph{Constructions handled by UD.}  A number of constructions
that are especially common in tweets are well handled by UD
conventions: ellipsis, irregular word orders, and paratactic sentences \yicomment{or phrases/components}
not explicitly delineated by punctuation.

@@

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is an at-mention %(followed by a colon \nascomment{?})
as a sign that a tweet is a reply to a tweet by the mentioned user\yicomment{not necessary, can be just mentioning somebody. should be careful to say it. We can say this construction include 1. reply;  2. mention sb. Both cases are similar to general vocative proper noun case in standard texts. And we need to exclude at-mentions in Retweet Construction.}.  We
treat these at-mentions as vocative expressions, labeling them as
\emph{proper noun} (\texttt{PROPN})\yicomment{here is confusing that PROPN could be thought as a label in dependencies.} and attaching them to the
following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example) \yicomment{just as UD guidelines}.

@@

\subsection{\sc Tweebank v2}\label{sec:anno-process}
Following the guidelines presented above, we create a new annotated\yicomment{del?} Twitter \yicomment{Twitter dependency?} treebank, which we call {\sc Tweebank v2}.

@@

\subsubsection{Annotation Process}
Our annotation process was conducted in three stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
proportion and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the \yicomment{general} UD
annotation conventions and our guidelines \yicomment{specifically for annotating tweets}.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and
parser were trained on the annotated data from the first stage (1,050 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data. Finally, an extra
layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)} was manually annotated for data
analysis purposes. For example, {\em idc} is annotated as
`I\_don't\_care' and {\em 4 my FAM} is as `for my familiy'.
Such normalization doesn't change our tokenization annotation. \yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them.}\yjcomment{add ``a tokenizer''}
\yicomment{add final data split} We obtained 3,550 labelled annotated tweets, split into train/dev/test set with /(639 $+$ 1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new tweets from the Twitter stream. \yicomment{should also mention main annotators (authors) are non-native English speakers?}

@@

We trained our tokenizer on the training portion\yicomment{set?} of
\textsc{Tweebank v2} combined with the UD\_English training dataset
and tested on the \textsc{Tweebank v2} test set. 
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with the UD pipe, we use LSTM
instead of GRU in our model and we also use a larger size of hidden units (64 against 20),
which has stronger representation power. \nascomment{we need to say what their model was;
  why does ours work better?  from their paper, it seems that they
  used a GRU instead of an LSTM ... is that all?  do we win because of
better tuning, or what?}\yjcomment{done.}
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

Results of the \citet{owoputi-EtAl:2013:NAACL-HLT}  with non-greedy
inference on automatically tokenized data
are shown in  Table \ref{tbl:pos-result-vs-tok}.  We see that errors
in tokenization do propagate, but tagging performance is above 93\%
with our tokenizer. \yicomment{our POS tagger results on automatically tokenized data?}

@@

\paragraph{Ensemble.}  Due both\yicomment{?} to ambiguity in the training
data---which most loss functions are not robust to \citep{Frnay2014ClassificationIT}, including the log loss we use, following
\citet{ballesteros-dyer-smith:2015:EMNLP}---and due to the instability
of neural network training, we follow \citet{Dietterich2000} and
consider an ensemble of twenty parsers trained using different random
initialization.  To parse at test time, the transition probabilities of the twenty
members of the ensemble are averaged.  The result achieves LAS of
79.4, outperforming all three systems above (Table~\ref{tbl:parse-result}).
However, ensembling 20 parsers also significantly slows down the parsing
speed and leads to the slowest system in our comparison.
